---
title: "volcanoes1"
author: "Annika Weber"
date: "2022-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(tidyverse)
library(dplyr)
```
```

```{r}
volcano <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-12/volcano.csv')

indonesia_volcanoes1 <- volcano %>% 
  filter(country == "Indonesia") 

#created popup info and made bold letters and line break
indonesia_volcanoes1 <- indonesia_volcanoes1 %>% 
  mutate(popup_info = paste("<b>Volcano Name:</b>", `volcano_name`, "<br/>",
                            "<b>Last Eruption:</b>", last_eruption_year, "<br/>",
                            "<b>Elevation:</b>", elevation, "meters"))
#created leaflet                            
leaflet() %>% 
  addProviderTiles("CartoDB.DarkMatter") %>% 
  addCircleMarkers(data = indonesia_volcanoes1, 
                   lat = ~ latitude, 
                   lng = ~ longitude, radius = 3, 
                   popup = ~popup_info, 
                   color = "red")
                                         

```

